Are We Reusing Outdated Code from Stack Overflow?

### 2016-11-05 latex-acm/cloneoverflow.tex
Updated sankey diagram and latex file

	\caption{109 Qualitas projects (new versions retrieved on 2016-09-27)}
	\label{t:new_and_old}
%	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|c|c|p{3cm}|p{3cm}}
			Projects & Old version & New versions & Latest change & CVS & License & Notes \\
			antlr4 & 4.0 & 4.5.4 & 25/09/2016 & git & BSD & \\
			apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & git & Apache2.0 & \\
			argouml & 0.34 & 0.35.4 & 11/01/2015 	& svn & Eclipse  1.0 & \\
			artofillusion & 2.8.1 & 3.0.2 & 27/08/2016 & svn & GPL 2.0 & \\
			aspectj & 1.6.9 & 1.8.9 & 12/05/2016 & git & Eclipse   1.0 & \\
			axion & 1.0-M2 & - & 08/03/2013 & - & Proprietary (BSD/Apache-style) & \\
			batik & 1.7 & 1.9.0 & 11/05/2016 & svn & Apache , v.2.0 & \\
			c-jdbc & 2.0.2 & - & 16/09/2005 & - & GLGPL 2.1 & \\
			castor & 1.3.1 & 1.4.2 & 17/08/2016 & git & Apache 2.0 & \\
			cayenne & 3.0.1 & 4.0.M4 &  26/09/2016 & git & Apache 2.0 & \\
			checkstyle & 5.1 & 7.2  & 23/09/2016 & git & GLGPL 2.1 \& Apache 2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
			cobertura & 1.9.4.1 & 2.1.2 & 01/06/2016 & git & GPL 2.0  & \\
			colt & 1.2.0 & - & 09/09/2014 & - & Proprietary (CERN) & Found multithreaded v. \\
			columba & 1.4 & - & 20/04/2007 & - & Mozilla   1.1  & \\
			commons-collections & 3.2.1 & 4.2 & 12/09/2016 & svn & Apache 2.0 & \\
			compiere & 330 & - & - & - & GPL 2.0 & No longer OSS \\
			db-derby & 10.6.1.0 & 10.12.1 & 13/08/2016 & svn & Apache 2.0 & \\
			displaytag & 1.2 & 2.0 & 17/08/2014 & svn & MIT  & \\
			drawswf & 1.2.9 & - & 02/04/2013 & - & GPL 2.0 & \\
			drjava & 20100913-r5387 & ??? & 03/09/2014 & svn & BSD  & Build to see version? \\
			exoportal & ??? & ??? &  & git & GLGPL 3.0 \& proprietary & Too many new projects \\
			emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & - & Common   1.0 & \\
			findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & - & GLGPL 2.0 & \\
			fit-java & 1.1 & - & 04/06/2013 & - & GPL 2.0 & \\
			fitlibrary & 20100806 & ??? & 29/07/2014 & git & GPL 2.0 & \\
			freecol & 0.10.7 & 0.11.6 & 26/09/2016 & git & GPL 2.0 &  \\
			freecs & 1.3.20100406 & - & 22/04/2013 & - & GPL 3.0 &   \\
			freemind & 0.9.0 & 1.0.0 & 16/08/2016 & git & GPL 2.0+ &  \\
			galleon & 2.3.0 & 2.5.6 & 29/04/2013 & - & GPL 2.0 & \\
			ganttproject & 2.0.9 & 2.8.1 & 16/08/2016 & git & GPL 3.0 &  \\
			geotools & 2.7-M3 & 16 & 27/09/2016 & git & GLGPL 2.0 & \\
			hadoop & 1.0.0 & 3.0.0-alpha2 & 26/09/2016 & git & Apache 2.0 & \\
			heritrix & 1.14.4 & - & 05/06/2013 & - & GLGPL 2.1 & \\
			hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & GLGPL 2.1+ & \\
			hsqldb & 2.0.0 & 2.3.4 & 13/09/2016 & svn & BSD  & \\
			htmlunit & 2.8 & 2.24 & 26/09/2016 & svn & Apache 2.0 & \\
			ireport & 3.7.5 & - & 28/05/2014 & - & Affero GLGPL 3.0 & \\
			itext & 5.0.3 & 5.5.9 & 27/09/2016 & git & Affero GLGPL 3.0 & \\
			informa & 0.7.0-alpha2 & - & 07/11/2008 & - & GLGPL 2.1 \& Apache Software 1.1 & \\
			ivatagroupware & 0.11.3 & - & 27/02/2013 & - & GPL 2.0 & \\
			jfin\_datemath & R1\_0\_1 & - & 25/04/2013 & - & GPL 2.0 & \\
			joggplayer & 114s & - &  15/04/2013 & - & GPL 2.0 & \\
			jag & 6.1 & 6.2 & 08/04/2013  & - & GPL 2.0 \& BSD  & BSD  is for libraries. \\
			james & 2.2.0 & 2.3.2.1 & 14/08/2015 & - & Apache 2.0 & \\
			jasml & 0.10 & - & 08/03/2013 & - & Apache Software  & \\
			jasperreports & 3.7.4 & 6.3.1 & 27/09/2016 & git & GLGPL 3.0 &  \\
			javacc & 5.0.0 & 7.0.0 & 15/08/2016 & svn & Proprietary (Sun) & \\
			jboss (wildfly) & 5.1.0.GA & 11.0.0.Alpha1 & 27/09/2016 & git & GLGPL 2.1 & Renamed to Wildfly. \\
			jchempaint & 3.0.1 & 3.4 & 01/09/2016 & git & GLGPL 2.1+ &  \\
			jedit & 4.3.2 & 5.3.1 & 20/09/2016 & svn & GPL 2.0 &  \\
			jena & 2.6.3 & 3.1.1 & 16/09/2016 & git & Apache 2.0 & \\
			jext & 5.0 & - & 18/08/2004 & - & GPL 2.0 &  \\
			jfreechart & 1.0.13 & 1.5.0 & 29/08/2016 & git & GLGPL 2.0 &   \\
			jgraph & 5.13.0.0 & 3.6.0.0 & 07/09/2016 & git & Proprietary (mxGraph) & \\
			jgraphpad & 5.10.0.2 & - & 10/11/2006 & - & GPL   \& GLGPL (derivatives) & \\
			jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & GLGPL 2.1 \& Eclipse  1.0 & \\
			jgroups & 2.10.0.GA & 4.0.0 & 26/09/2016 & git & Apache 2.0 & \\
			jmoney & 0.4.4 & ??? & 27/12/2015 & git & GPL 2.0 &  \\
			jparse & 0.96 & - & 29/07/2004 & - & GLGPL 2.1 & \\
			jpf & 1.5.1 & ??? & 13/01/2012 & - & Apache 2.0 & \\
			junit & 4.11 & 4.12 & 04/12/2014 & git & Eclipse  1.0 & \\
			shiftone-jrat & 0.6 & 1-beta-1 & 17/11/2007 & svn & GLGPL 2.0 &  \\
			vuze & 4812 & 5730 & 23/09/2016 & svn & GPL 2.0 & \\
		\end{tabular} %
%	}

\begin{table*}
	\centering
	\caption{109 Qualitas projects (new versions retrieved on 2016-09-27)}
	\label{t:new_and_old}
	%	\resizebox{\columnwidth}{!}{%
	\small
	\begin{tabular}{l|r|r|c|c|p{3cm}|p{3cm}}
		\hline 
			Projects & Old version & New versions & Latest change & CVS & License & Notes \\
			\hline
			apache-jmeter & 2. 9 & & & & & \\
			apache-log4j & 1.2.16 & & & & & \\
			apache-maven & 3.0 & & & & & \\
			apache-roller & 4.0.1 & & & & & \\
			apache-tomcat & 7.0.2 & & & & & \\
			jhotdraw & 7.5.1 & & & & & \\
			jrefactory & 2.9.19 & & & & & \\
			jruby & 1.5.2 & & & & & \\
			jspwiki & 2.8.4 & & & & & \\
			jstock & 1.0.7c & & & & & \\
			jsxe & 04\_beta & & & & & \\
			jtopen & 7\_1 & & & & & \\
			jung2 & 2\_0\_1 & & & & & \\
			lucene & 4.3.0 & & & & & \\
			marauroa & 3.8.1 & & & & & \\
			megamek & 0.35.18 & & & & & \\
			mvnforum (mvnad) & 1.2.2 (1.0.1) & & & & & \\
			myfaces-core & 2.0.2 & & & & & \\
			nakedobjects & 4.0.0 & & & & & \\
			nekohtml & 1.9.14 & & & & & \\
			netbeans & 6.9.1 & & & & & \\
			openjms & 0.7.7-beta-1 & & & & & \\
			oscache & 2.4.1 & & & & & \\
			picocontainer & 2.10.2 & & & & & \\
			pmd & 4.2.5 & & & & & \\
			poi & 3.6 & & & & & \\
			pooka & 080505 & & & & & \\
			proguard & 4.5.1 & & & & & \\
			quartz & 1.8.3 & & & & & \\
			quickserver & 1.4.7 & & & & & \\
			quilt & 0.6-a-5 & & & & & \\
			rssowl & 2.0.5 & & & & & \\
			sablecc & 3.2 & & & & & \\
			sandmark & & & & & & \\
			spring-framework & 3.0.5 & & & & & \\
			struts2 & 2.2.1-all & & & & & \\
			sunflow & 0.07.2 & & & & & \\
			tapestry & 5.1.0.5 & & & & & \\
			trove & 2.1.0 & & & & & \\
			velocity & 1.6.4 & & & & & \\
			wct-package & 1.5.2 & & & & & \\
			webmail & 0.7.10 & & & & & \\
			weka & 3-7-9 & & & & & \\
			xalan-j & 2\_7\_1 & & & & & \\
			xerces-J & 2.10.0 & & & & & \\
			xmojo & 5.0.0 & & & & & \\
			\hline 
		\end{tabular} %
%	}
\end{table*}

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\linewidth]{Sankey_proj}
	\caption{Relationships between 184 true online code clone found between Stack Overflow and Qualitas projects}
	\label{fig:sankey}
\end{figure*}

@@

The manual investigation of 48 class-A online clone pairs reveals that there are 30 stale clones. They are clone pairs that were copied from Qualitas projects to Stack Overflow and marked as \textit{accepted} answers.  The investigation results are described in Table \ref{tab:stale_code}.

\begin{table}
	\centering
	\caption{Summary of stale code clones found}
	\label{tab:stale_code}
	\small
	\begin{tabular}{l|r|r|r}
		\hline 
		Project & Pairs & Stale & Fresh \\
		\hline
		apache-ant & 1 & 0 & 1 \\
		aspectj & 2 & 2 & 0 \\
		hadoop & 14 & 9 & 5 \\
		hibernate & 16 & 5 & 11 \\
		jasperreports & 2 & 2 & 0 \\
		jfreechart & 4 & 4 & 0 \\
		jgraph & 5 & 5 & 0 \\
		jgrapht & 1 & 0 & 1 \\
		junit & 3 & 3 & 0 \\
		\hline
		Total & 48 & 30 & 18 \\
		\hline
	\end{tabular} 
\end{table}

\begin{table*}
	\centering
	\caption{30 stale code clones in Stack Overflow found by a manual investigation}
	\label{tab:stale_code_details}
	\small
	\begin{tabular}{r|l|r|c|l}
		\hline 
		No. & File & Stack Overflow Q\&A & Changes made & Date \\
		\hline
		1 & aspectjtools1.6.9-src/../Agent.java & 18303692 & alteration & 2015-09-08 \\
		2 & aspectjweaver1.6.9-src/../Agent.java & 18303692 & alteration & 2015-09-08 \\
		3 & hadoop-1.0.0/../WritableComparator.java & 22315734 & alteration & 2014-11-20 \\
		4 & hadoop-1.0.0/../StringUtils.java & 801987 & alteration & 2013-02-04 \\
		5 & hadoop-1.0.0/../DBCountPageView.java & 21702608 & alteration & 2011-06-12 \\
		6 & hadoop-1.0.0/../DBCountPageView.java & 21702608 & alteration & 2011-06-12 \\
		7 & hadoop-1.0.0/../LineRecordReader.java & 16180910 & alteration & 2011-07-25 \\
		8 & hadoop-1.0.0/../LineRecordReader.java & 16180910 & alteration & 2011-07-25 \\
		9 & hadoop-1.0.0/../JobSubmissionFiles.java & 14845581 & alteration & 2012-06-25 \\
		10 & hadoop-1.0.0/../TextOutputFormat.java & 16928749 & alteration & 2011-06-12 \\
		11 & hadoop-1.0.0/../TestJobCounters.java & 18833798 & alteration & 2011-06-12 \\
		12 & hibernate-release-4.2.2.Final/../SettingsFactory.java & 8257554 & removal & 2011-03-11 \\
		13 & hibernate-release-4.2.2.Final/../Example.java & 24924255 & alteration & 2013-04-23 \\
		14 & hibernate-release-4.2.2.Final/../SQLServer2005LimitHandler.java.java & 23967852 & alteration & 2013-04-23 \\
		15 & hibernate-release-4.2.2.Final/../ConnectionProviderInitiator.java & 15168494 & alteration & 2016-02-24 \\
		16 & hibernate-release-4.2.2.Final/../SchemaUpdate.java & 23520731 & alteration & 2016-02-05 \\
		17 & jasperreports-3.7.4/../JRVerifier.java & 8037824 & removal & 2011-05-20 \\
		18 & jasperreports-3.7.4/../JRVerifier.java & 8037824 & alteration & 2013-12-08 \\
		19 & jasperreports-3.7.4/../SpiderWebPlot.java & 21998949 & alteration & 2013-11-22 \\
		20 & jasperreports-3.7.4/../SpiderWebPlot.java & 21998949 & alteration & 2013-11-22 \\
		21 & jasperreports-3.7.4/../AbstractXYItemRenderer.java & 12936580 & alteration & 2016-01-16 \\
		22 & jfreechart-1.0.13/../KeyToGroupMap.java & 16058183 & alteration & 2013-07-03 \\
		23 & jgraph-latest-bsd-src/../GroupingRemoving.java & 6722760 & rewriting & 2005 \\
		24 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & rewriting & 2005 \\
		25 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & rewriting & 2005 \\
		26 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & rewriting & 2005 \\
		27 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & rewriting & 2005 \\
		28 & junit-4/org/junit/Assert.java & 23586872 & alteration & 2015-05-12 \\
		29 & junit-4/../ExpectException.java & 8802082 & alteration & 2014-05-26 \\
		30 & junit-4/../ExternalResource.java & 7504040 & alteration & 2016-06-25 \\
		\hline
	\end{tabular} 
\end{table*}

>>>>

%	\caption{109 Qualitas projects (new versions retrieved on 2016-09-27)}
%	\label{t:new_and_old}
%%	\resizebox{\columnwidth}{!}{%
%	\small
%		\begin{tabular}{l|r|r|c|c|p{3cm}|p{3cm}}
%			Projects & Old version & New versions & Latest change & CVS & License & Notes \\
%			antlr4 & 4.0 & 4.5.4 & 25/09/2016 & git & BSD & \\
%			apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & git & Apache2.0 & \\
%			argouml & 0.34 & 0.35.4 & 11/01/2015 	& svn & Eclipse  1.0 & \\
%			artofillusion & 2.8.1 & 3.0.2 & 27/08/2016 & svn & GPL 2.0 & \\
%			aspectj & 1.6.9 & 1.8.9 & 12/05/2016 & git & Eclipse   1.0 & \\
%			axion & 1.0-M2 & - & 08/03/2013 & - & Proprietary (BSD/Apache-style) & \\
%			batik & 1.7 & 1.9.0 & 11/05/2016 & svn & Apache , v.2.0 & \\
%			c-jdbc & 2.0.2 & - & 16/09/2005 & - & GLGPL 2.1 & \\
%			castor & 1.3.1 & 1.4.2 & 17/08/2016 & git & Apache 2.0 & \\
%			cayenne & 3.0.1 & 4.0.M4 &  26/09/2016 & git & Apache 2.0 & \\
%			checkstyle & 5.1 & 7.2  & 23/09/2016 & git & GLGPL 2.1 \& Apache 2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
%			cobertura & 1.9.4.1 & 2.1.2 & 01/06/2016 & git & GPL 2.0  & \\
%			colt & 1.2.0 & - & 09/09/2014 & - & Proprietary (CERN) & Found multithreaded v. \\
%			columba & 1.4 & - & 20/04/2007 & - & Mozilla   1.1  & \\
%			commons-collections & 3.2.1 & 4.2 & 12/09/2016 & svn & Apache 2.0 & \\
%			compiere & 330 & - & - & - & GPL 2.0 & No longer OSS \\
%			db-derby & 10.6.1.0 & 10.12.1 & 13/08/2016 & svn & Apache 2.0 & \\
%			displaytag & 1.2 & 2.0 & 17/08/2014 & svn & MIT  & \\
%			drawswf & 1.2.9 & - & 02/04/2013 & - & GPL 2.0 & \\
%			drjava & 20100913-r5387 & ??? & 03/09/2014 & svn & BSD  & Build to see version? \\
%			exoportal & ??? & ??? &  & git & GLGPL 3.0 \& proprietary & Too many new projects \\
%			emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & - & Common   1.0 & \\
%			findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & - & GLGPL 2.0 & \\
%			fit-java & 1.1 & - & 04/06/2013 & - & GPL 2.0 & \\
%			fitlibrary & 20100806 & ??? & 29/07/2014 & git & GPL 2.0 & \\
%			freecol & 0.10.7 & 0.11.6 & 26/09/2016 & git & GPL 2.0 &  \\
%			freecs & 1.3.20100406 & - & 22/04/2013 & - & GPL 3.0 &   \\
%			freemind & 0.9.0 & 1.0.0 & 16/08/2016 & git & GPL 2.0+ &  \\
%			galleon & 2.3.0 & 2.5.6 & 29/04/2013 & - & GPL 2.0 & \\
%			ganttproject & 2.0.9 & 2.8.1 & 16/08/2016 & git & GPL 3.0 &  \\
%			geotools & 2.7-M3 & 16 & 27/09/2016 & git & GLGPL 2.0 & \\
%			hadoop & 1.0.0 & 3.0.0-alpha2 & 26/09/2016 & git & Apache 2.0 & \\
%			heritrix & 1.14.4 & - & 05/06/2013 & - & GLGPL 2.1 & \\
%			hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & GLGPL 2.1+ & \\
%			hsqldb & 2.0.0 & 2.3.4 & 13/09/2016 & svn & BSD  & \\
%			htmlunit & 2.8 & 2.24 & 26/09/2016 & svn & Apache 2.0 & \\
%			ireport & 3.7.5 & - & 28/05/2014 & - & Affero GLGPL 3.0 & \\
%			itext & 5.0.3 & 5.5.9 & 27/09/2016 & git & Affero GLGPL 3.0 & \\
%			informa & 0.7.0-alpha2 & - & 07/11/2008 & - & GLGPL 2.1 \& Apache Software 1.1 & \\
%			ivatagroupware & 0.11.3 & - & 27/02/2013 & - & GPL 2.0 & \\
%			jfin\_datemath & R1\_0\_1 & - & 25/04/2013 & - & GPL 2.0 & \\
%			joggplayer & 114s & - &  15/04/2013 & - & GPL 2.0 & \\
%			jag & 6.1 & 6.2 & 08/04/2013  & - & GPL 2.0 \& BSD  & BSD  is for libraries. \\
%			james & 2.2.0 & 2.3.2.1 & 14/08/2015 & - & Apache 2.0 & \\
%			jasml & 0.10 & - & 08/03/2013 & - & Apache Software  & \\
%			jasperreports & 3.7.4 & 6.3.1 & 27/09/2016 & git & GLGPL 3.0 &  \\
%			javacc & 5.0.0 & 7.0.0 & 15/08/2016 & svn & Proprietary (Sun) & \\
%			jboss (wildfly) & 5.1.0.GA & 11.0.0.Alpha1 & 27/09/2016 & git & GLGPL 2.1 & Renamed to Wildfly. \\
%			jchempaint & 3.0.1 & 3.4 & 01/09/2016 & git & GLGPL 2.1+ &  \\
%			jedit & 4.3.2 & 5.3.1 & 20/09/2016 & svn & GPL 2.0 &  \\
%			jena & 2.6.3 & 3.1.1 & 16/09/2016 & git & Apache 2.0 & \\
%			jext & 5.0 & - & 18/08/2004 & - & GPL 2.0 &  \\
%			jfreechart & 1.0.13 & 1.5.0 & 29/08/2016 & git & GLGPL 2.0 &   \\
%			jgraph & 5.13.0.0 & 3.6.0.0 & 07/09/2016 & git & Proprietary (mxGraph) & \\
%			jgraphpad & 5.10.0.2 & - & 10/11/2006 & - & GPL   \& GLGPL (derivatives) & \\
%			jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & GLGPL 2.1 \& Eclipse  1.0 & \\
%			jgroups & 2.10.0.GA & 4.0.0 & 26/09/2016 & git & Apache 2.0 & \\
%			jmoney & 0.4.4 & ??? & 27/12/2015 & git & GPL 2.0 &  \\
%			jparse & 0.96 & - & 29/07/2004 & - & GLGPL 2.1 & \\
%			jpf & 1.5.1 & ??? & 13/01/2012 & - & Apache 2.0 & \\
%			junit & 4.11 & 4.12 & 04/12/2014 & git & Eclipse  1.0 & \\
%			shiftone-jrat & 0.6 & 1-beta-1 & 17/11/2007 & svn & GLGPL 2.0 &  \\
%			vuze & 4812 & 5730 & 23/09/2016 & svn & GPL 2.0 & \\
%		\end{tabular} %
%%	}

\begin{table*}
	\centering
	\caption{17 selected Qualitas projects (new versions retrieved on 2016-09-27)}
	\label{t:new_and_old}
	%	\resizebox{\columnwidth}{!}{%
	\small
	\begin{tabular}{l|r|r|c|c|p{3cm}}
		\hline 
		Projects & Old version & New versions & Latest change & CVS & License  \\
		\hline
		apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & git & Apache2.0 \\
		apache-log4j & 1.2.16 & & & & \\
		apache-tomcat & 7.0.2 & & & & \\
		aspectj & 1.6.9 & 1.8.9 & 12/05/2016 & git & Eclipse 1.0 \\
		hadoop & 1.0.0 & 3.0.0-alpha2 & 26/09/2016 & git & Apache 2.0\\
		hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & GLGPL 2.1+ \\
		jasperreports & 3.7.4 & 6.3.1 & 27/09/2016 & git & GLGPL 3.0  \\
		jfreechart & 1.0.13 & 1.5.0 & 29/08/2016 & git & GLGPL 2.0  \\
		jgraph & 5.13.0.0 & 3.6.0.0 & 07/09/2016 & git & Proprietary (mxGraph) \\
		jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & GLGPL 2.1 \& Eclipse  1.0 \\
		jstock & 1.0.7c & & & & \\
		jung2 & 2\_0\_1 & & & & \\
		junit & 4.11 & 4.12 & 04/12/2014 & git & Eclipse  1.0 \\
		poi & 3.6 & & & & \\
		spring-framework & 3.0.5 & & & & \\
		struts2 & 2.2.1-all & & & & \\
		weka & 3-7-9 & & & & \\
		\hline
	\end{tabular} %
	%	}
\end{table*}

%\begin{table*}
%	\centering
%	\caption{109 Qualitas projects (new versions retrieved on 2016-09-27)}
%	\label{t:new_and_old}
%	%	\resizebox{\columnwidth}{!}{%
%	\small
%	\begin{tabular}{l|r|r|c|c|p{3cm}|p{3cm}}
%		\hline 
%			Projects & Old version & New versions & Latest change & CVS & License & Notes \\
%			\hline
%			apache-jmeter & 2. 9 & & & & & \\
%			apache-log4j & 1.2.16 & & & & & \\
%			apache-maven & 3.0 & & & & & \\
%			apache-roller & 4.0.1 & & & & & \\
%			apache-tomcat & 7.0.2 & & & & & \\
%			jhotdraw & 7.5.1 & & & & & \\
%			jrefactory & 2.9.19 & & & & & \\
%			jruby & 1.5.2 & & & & & \\
%			jspwiki & 2.8.4 & & & & & \\
%			jstock & 1.0.7c & & & & & \\
%			jsxe & 04\_beta & & & & & \\
%			jtopen & 7\_1 & & & & & \\
%			jung2 & 2\_0\_1 & & & & & \\
%			lucene & 4.3.0 & & & & & \\
%			marauroa & 3.8.1 & & & & & \\
%			megamek & 0.35.18 & & & & & \\
%			mvnforum (mvnad) & 1.2.2 (1.0.1) & & & & & \\
%			myfaces-core & 2.0.2 & & & & & \\
%			nakedobjects & 4.0.0 & & & & & \\
%			nekohtml & 1.9.14 & & & & & \\
%			netbeans & 6.9.1 & & & & & \\
%			openjms & 0.7.7-beta-1 & & & & & \\
%			oscache & 2.4.1 & & & & & \\
%			picocontainer & 2.10.2 & & & & & \\
%			pmd & 4.2.5 & & & & & \\
%			poi & 3.6 & & & & & \\
%			pooka & 080505 & & & & & \\
%			proguard & 4.5.1 & & & & & \\
%			quartz & 1.8.3 & & & & & \\
%			quickserver & 1.4.7 & & & & & \\
%			quilt & 0.6-a-5 & & & & & \\
%			rssowl & 2.0.5 & & & & & \\
%			sablecc & 3.2 & & & & & \\
%			sandmark & & & & & & \\
%			spring-framework & 3.0.5 & & & & & \\
%			struts2 & 2.2.1-all & & & & & \\
%			sunflow & 0.07.2 & & & & & \\
%			tapestry & 5.1.0.5 & & & & & \\
%			trove & 2.1.0 & & & & & \\
%			velocity & 1.6.4 & & & & & \\
%			wct-package & 1.5.2 & & & & & \\
%			webmail & 0.7.10 & & & & & \\
%			weka & 3-7-9 & & & & & \\
%			xalan-j & 2\_7\_1 & & & & & \\
%			xerces-J & 2.10.0 & & & & & \\
%			xmojo & 5.0.0 & & & & & \\
%			\hline 
%		\end{tabular} %
%%	}
%\end{table*}

@@

\begin{figure}
	\centering
	\includegraphics[width=1.2\linewidth]{Sankey_proj}
	\caption{Relationships of 49 outdated clone pairs and 4 deleted clone pairs (depicted using (d) suffix)}
	\label{fig:sankey}
\end{figure}

@@

Table \ref{tab:stale_code} shows the results of manual investigation of 84 class-A online clone pairs. The investigation reveals that there are 50 clone pairs that are outdate (i.e. ``stale clone''). They are clone pairs that were copied from Qualitas projects to Stack Overflow and marked as \textit{accepted} answers, and later have been changed during the development.

\begin{table}
	\centering
	\caption{Results from a manual investigation of 84 class-A online clone pairs}
	\label{tab:stale_code}
	\small
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r}
		\hline 
		Project & Pairs & Stale & Fresh & Del. & Others \\
		\hline
		ant & 1 & 0 & 1 & 0 & 0 \\
		log4j & 4 & 0 & 4 & 0 & 0 \\
		tomcat & 7 & 7 & 0 & 0 & 0 \\
		aspectj & 2 & 2 & 0 & 0 & 0 \\
		hadoop & 14 & 9 & 5 & 0 & 0 \\
		hibernate & 16 & 4 & 11 & 1 & 0 \\
		jasperreports & 2 & 2 & 0 & 0 & 0 \\
		jfreechart & 4 & 4 & 0 & 0 & 0 \\
		jgraph & 5 & 4 & 0 & 0 & 1 \\
		jgrapht & 1 & 0 & 1 & 0 & 0 \\
		jstock & 2 &  2 & 0 & 0 & 0 \\
		jung & 2 & 2 & 0 & 0 & 0 \\
		junit & 3 & 3 & 0 & 0 & 0 \\
		poi & 3 & 1 & 2 & 0 & 0 \\
		spring & 14 & 9 & 3 & 2 & 0 \\
		struts & 1 & 1 & 0 & 0 & 0 \\
		weka & 3 & 0 & 3 & 0 & 0 \\
		\hline
		Total & 84 & 50 & 30 & 3 & 1 \\
		\hline
	\end{tabular} 
}
\end{table}
	\caption{53 code clones in Stack Overflow that were altered, rewritten, or removed from the project after posted}
	\label{tab:stale_code_details}
	\begin{tabular}{r|l|l|r|c|l}
		No. & Project & File & SO Post & Changes & Date \\
		1 &  aspectj-1.6.9  &  Agent.java  & 18303692 &  alteration  & 2015-09-08 \\
		2 &  aspectj-1.6.9   &  Agent.java  & 18303692 &  alteration  & 2015-09-08 \\
		3 &  hadoop-1.0.0  &  DBCountPageView.java  & 21702608 &  alteration & 2011-06-12 \\
		4 &  hadoop-1.0.0  &  DBCountPageView.java  & 21702608 &  alteration  & 2011-06-12 \\
		5 &  hadoop-1.0.0  &  JobSubmissionFiles.java  & 14845581 &  alteration  & 2012-06-25 \\
		6 &  hadoop-1.0.0  &  LineRecordReader.java  & 16180910 &  alteration & 2011-07-25 \\
		7 &  hadoop-1.0.0  &  LineRecordReader.java  & 16180910 &  alteration  & 2011-07-25 \\
		8 &  hadoop-1.0.0  &  StringUtils.java  & 801987 &  alteration & 2013-02-04 \\
		9 &  hadoop-1.0.0  &  TestJobCounters.java  & 18833798 &  alteration  & 2011-06-12 \\
		10 &  hadoop-1.0.0  &  TextOutputFormat.java  & 16928749 &  alteration  & 2011-06-12 \\
		11 &  hadoop-1.0.0  &  WritableComparator.java  & 22315734 &  alteration & 2014-11-20 \\
		12 &  hibernate-4.2.2  &  ConnectionProviderInitiator.java  & 15168494 &  alteration  & 2012-06-24 \\
		13 &  hibernate-4.2.2  &  Example.java  & 24924255 &  alteration  & 2013-04-23 \\
		14 &  hibernate-4.2.2  &  SchemaUpdate.java  & 23520731 &  alteration & 2016-02-05 \\
		15 &  hibernate-4.2.2  &  SettingsFactory.java  & 8257554 &  removal & 2011-03-11 \\
		16 &  hibernate-4.2.2  &  SQLServer2005LimitHandler.java  & 23967852 &  alteration  & 2015-03-12 \\
		17 &  jasperreports-3.7.4  &  JRVerifier.java  & 8037824 &  alteration  & 2008-04-17 \\
		18 &  jasperreports-3.7.4  &  JRVerifier.java  & 8037824 &  alteration & 2011-05-20 \\
		19 &  jfreechart-1.0.13  &  AbstractXYItemRenderer.java  & 12936580 &  alteration  & 2016-02-19 \\
		20 &  jfreechart-1.0.13  &  KeyToGroupMap.java  & 16058183 &  alteration  & 2013-07-03 \\
		21 &  jfreechart-1.0.13  &  SpiderWebPlot.java  & 21998949 &  alteration  & 2008-06-02 \\
		22 &  jfreechart-1.0.13  &  SpiderWebPlot.java  & 21998949 &  alteration  & 2008-06-02 \\
		23 &  jgraph-5.13.0.0  &  HelloWorld.java  & 6722760 &  rewriting  & 2014-04-13 \\
		24 &  jgraph-5.13.0.0  &  HelloWorld.java  & 6722760 &  rewriting  & 2014-04-13 \\
		25 &  jgraph-5.13.0.0  &  HelloWorld.java  & 6722760 &  rewriting  & 2014-04-13 \\
		26 &  jgraph-5.13.0.0  &  HelloWorld.java  & 6722760 &  rewriting  & 2014-04-13 \\
		27 &  jstock-1.0.7c  &  GoogleMail.java  & 14940863 &  alteration & 2015-12-13 \\
		28 &  jstock-1.0.7c  &  GoogleMail.java  & 24680923 &  alteration  & 2015-12-13 \\
		29 &  jung2-2\_0\_1  &  ShortestPathDemo.java  & 6025026 &  alteration  & 2010-04-13 \\
		30 &  jung2-2\_0\_1  &  ShortestPathDemo.java  & 6025026 &  alteration  & 2010-04-13 \\
		31 &  junit-4  &  Assert.java  & 23586872 &  alteration  & 2015-05-12 \\
		32 &  junit-4  &  ExternalResource.java  & 7504040 &  alteration & 2016-06-25 \\
		33 &  junit-4.11  &  ExpectException.java  & 8802082 &  alteration & 2014-05-26 \\
		34 &  poi-3.6-20091214  &  WorkbookFactory.java  & 12593810 &  alteration  & 2015-04-29 \\
		35 &  spring-framework-3.0.5  &  AnnotationMethodHandlerExceptionResolver.java  & 5660519 &  removal & 2012-01-20 \\
		36 &  spring-framework-3.0.5  &  AutowireUtils.java  & 20913543 &  alteration  & 2014-10-28 \\
		37 &  spring-framework-3.0.5  &  CustomCollectionEditor.java  & 18623736 &  alteration  & 2013-11-21 \\
		38 &  spring-framework-3.0.5  &  DefaultAnnotationHandlerMapping.java  & 3758110 &  removal  & 2012-01-20 \\
		39 &  spring-framework-3.0.5  &  DefaultPropertiesPersister.java  & 6149818 &  alteration  & 2013-03-19 \\
		40 &  spring-framework-3.0.5  &  DelegatingServletInputStream.java  & 20996373 &  alteration  & 2016-07-15 \\
		41 &  spring-framework-3.0.5  &  DelegatingServletInputStream.java  & 20996373 &  alteration  & 2008-12-18 \\
		42 &  spring-framework-3.0.5  &  DelegatingServletInputStream.java  & 20996373 &  alteration  & 2008-12-18 \\
		43 &  spring-framework-3.0.5  &  DispatcherServlet.java  & 4781746 &  alteration  & 2011-08-08 \\
		44 &  spring-framework-3.0.5  &  Jaxb2Marshaller.java  & 10924700 &  alteration  & 2012-08-28 \\
		45 &  spring-framework-3.0.5  &  ScheduledTasksBeanDefinitionParser.java  & 3751463 &  alteration  & 2016-07-05 \\
		46 &  struts2-2.2.1  &  DefaultActionMapper.java  & 14019840 &  alteration  & 2013-10-18 \\
		47 &  tomcat-7.0.2  &  BasicAuthenticator.java  & 21734562 &  alteration  & 2016-08-04 \\
		48 &  tomcat-7.0.2  &  BasicAuthenticator.java  & 21734562 &  alteration & 2016-08-04 \\
		49 &  tomcat-7.0.2  &  CoyoteAdapter.java  & 24404964 &  alteration  & 2012-11-18 \\
		50 &  tomcat-7.0.2  &  CoyoteAdapter.java  & 24404964 &  alteration  & 2012-11-18 \\
